%\thispagestyle{empty}
\fancyhead[C]{\zihao{5}  \songti 摘\hspace{1em}要}
\section*{\zihao{-3} \centering 情感挖掘技术在证券分析中的应用研究}
%\vspace{0.5cm}

\noindent
\section*{\zihao{-3} \centering \textbf{摘\hspace{1em}要}}

技术的快速发展改变了投资者社交和购买决策的动力。过去十年中，在线评论的数量迅速增长，导致投资者群体在购买决策过程中承担了不成比例的重量。对于运营商试图将评论纳入分析中来说，大量的评论可能是一项艰巨的任务。情感分析允许以相对容易且时间敏感的方式处理大量消费者评论。这些评论中包含的信息，情感分数，与其他消费者在做出购买决定之前从其他消费者那里收集到的情感相同。为了证明这些评论的重要性，本研究将试图使用消费者评论的情绪作为主要预测因素来股票价格的方向变化。本次研究从雪球网爬取的20只股票的历史价格信息和对应的投资者评论信息出发。对投资者的评论进行情感分析后采用MIC(最大信息系数)度量价格趋势和投资者态度之间的相关性。我们得出在线评论的消费者情绪将对股价的未来方向性趋势具有重要意义。

\vspace{0.5cm}
\noindent
\textbf{关键词：}情感挖掘 ；在线评论；数据处理；证券分析；MIC
%\addcontentsline{toc}{section}{摘要}%摘要是否包括进目录中

\clearpage

%\thispagestyle{empty}
\fancyhead[C]{\zihao{5}  \songti Abstract}
\section*{\songti\zihao{-3} \centering Research on the application of sentiment mining technology in stock analysis}

\section*{\zihao{-3} \textbf{Abstract}}
   %用了Times New Roman字体来美化观感
\noindent
The rapid development of technology has changed the dynamics of social and purchasing decisions for investors. The number of online reviews has grown rapidly over the past decade, leading to a disproportionate share of the weight of the investor community in the purchase decision process. A lot of comments can be a daunting task for operators trying to incorporate comments into their analysis. Affective analysis allows for a relatively easy and time-sensitive way to handle a large number of consumer reviews. These comments contain information about the same emotional score that other consumers collected from other consumers before making a purchase decision. To demonstrate the importance of these reviews, this study will attempt to use the sentiment of consumer commentary as a major predictor of the direction of stock price changes. This study starts with the historical price information of 20 stocks crawled by the snowball net and the corresponding investor's comment information. The relationship between the price trend and the investor's attitude is measured by the MIC (Maximum Information Coefficient) after the emotional analysis of the investor's comments. The consumer sentiment that we have come up with online commentary will be of great significance to the future directional trend of stock price.

\vspace{0.5cm}
\noindent
\textbf{Keywords: }Sentiment Analysis;Online Review; Data Processing; Stock Analysis; MIC
%\addcontentsline{toc}{section}{Abstract}%英文摘要是否包括进入目录
